### 2011-06-21 Paper/Paper.tex
non-functioning performance generator
Worked on repetition detection, fruitless

% Algorithm typesetting
\usepackage{algorithmic}

@@

\subsection{Related Work}
Move part of the introduction here?
\section{Approach}

\subsection{Score Model}
\subsubsection{Musical structure.}
When listening to music, the listener assigns a certain hierarchical structure to the music perceived: Notes make up phrases, phrases make up themes, themes make up parts and parts make up the piece. This structure is usually accentuated in a performance. The most obvious example of this is slowing down at the end of a piece. On a lower level, transitions between themes may be marked by slowing down, changing volume or changing speed. Although structure can be accentuated in a performance, listeners, and trained listeners even more so, will also be able to recognise structure in an expressionless reproduction of the score, or when quietly singing the music in their heads. This suggests that it is possible to extract structure from a merely score. It also seems likely that knowing the structure will help creating an expressive performance.

\paragraph*{Detecting repetition}

Similarity function based on rhythic pattern and melodic pattern.

@@

Consider the musical sequence $S = \{n_0, n_1, n_2, n_3\}$ is ambiguous and has two possible assignments of constituents: $S_0 = \{n_0\}, S_1 = \{n_1, n_2, n_3\}$ or $S'_0 = \{n_0, n_1\}, S'_1 = \{n_2, n_3\}$. The notion off repetition can help us here. Consider the case that $S'_1$ is a repetition of $S'_0$ but $S_1$ is not a repetition of $S_0$, this tells us that the split $S = \{S'_0, S'_1\}$ is more likely than the split $S = \{S_0, S_1\}$.

@@

>>>>

% Algorithm typesetting environments
\usepackage{algorithm}
\usepackage{algorithmic}

% Trees
\usepackage{qtree}

@@

\subsection{Related Work}
Move part of the introduction here?

\section{Approach}

\subsection{Musical structure}
When listening to music, the listener assigns a certain hierarchical structure to the music perceived: Notes make up phrases, phrases make up themes, themes make up parts and parts make up the piece. This structure is usually accentuated in a performance. The most obvious example of this is slowing down at the end of a piece. On a lower level, transitions between themes may be marked by slowing down, changing volume or changing speed. Although structure can be accentuated in a performance, listeners, and trained listeners even more so, will also be able to recognise structure in an expressionless reproduction of the score, or when quietly singing the music in their heads. This suggests that it is possible to extract structure from a merely score. It also seems likely that knowing the structure will help creating an expressive performance.

\subsubsection*{The delta framework}

The delta framework is based on the idea that small differences indicate low level structural transitions and large differences indicate higher level structural transitions.

\paragraph*{Combining delta trees}

In his MSc dissertation, van den Berg suggests using \textit{yeild rules} to combine trees generated by different delta functions. The yeild rule states that nodes in a set of trees can be connected if they are \textit{yeild equal}, that is, if the their set of leaf nodes they recursively contain is equal. The result is a multi-tree, in which the top note is always connected and intermediate nodes may or may not be connected.

Unfortunately, a multi tree is hard to interpret since

@@

Repetition be formulated in terms of the delta framework to provide greater generality. It seems desirable that we consider a transposed repetition of an earlier theme to be a repetition nevertheless. The same holds for rhythmic repetition: it may be that a particular rhythm is repeated, we want to treat this as a repetition too. The delta framework allows this intuition to be implemented easily: we only look at repetition in the deltas between notes. If we take for example the inter
---------------------------
Consider the musical sequence $S = \{n_0, n_1, n_2, n_3\}$ is ambiguous and has two possible assignments of constituents: $S_0 = \{n_0\}, S_1 = \{n_1, n_2, n_3\}$ or $S'_0 = \{n_0, n_1\}, S'_1 = \{n_2, n_3\}$. The notion off repetition can help us here. Consider the case that $S'_1$ is a repetition of $S'_0$ but $S_1$ is not a repetition of $S_0$, this tells us that the split $S = \{S'_0, S'_1\}$ is more likely than the split $S = \{S_0, S_1\}$.

@@

\begin{algorithm}
\begin{algorithmic}
\FOR{$\texttt{depth} \in \{\texttt{depth}(\texttt{tree}), \cdots, 0\}$}
  \FOR{$c \in \{c | \texttt{depth}(c, \texttt{tree}) = \texttt{depth}\}$}
    \FOR{$\texttt{class} \in C$}
      \IF{$\texttt{similar}(c, \texttt{class})$}
        \STATE c.class = class
      \ENDIF
    \ENDFOR
    \IF{c.class = null}
      \STATE C.append(createClass(c))
      \STATE c.class = createClass(c)
    \ENDIF
  \ENDFOR
\ENDFOR
\end{algorithmic}
\caption{Bottom up tree traversal and similarity relations}
\end{algorithm}

A resulting tree could look like figure \ref{similtree}

\begin{figure}
\begin{center}
\Tree 
[
.{$M$}
	[ .{$d$} 
		[ .{$a$} 
			[ .{$x$} ]
			[ .{$y$} ]
			[ .{$x$} ]
		]
		[ .{$a$} 
			[ .{$x$} ]
			[ .{$y$} ]
			[ .{$x$} ]
		]
	]	
	[ .{$e$} 
		[.{$c$} 
			[ .{$b$} 
				[ .{$p$} ]
				[ .{$q$} ]
			]
			[ .{$r$} ]
		]		
		[.{$a$} 
			[ .{$x$} ]
			[ .{$y$} ]
			[ .{$x$} ]
		]
	]
]
\end{center}
\caption{Example tree with similarities}
\label{similtree}
\end{figure}
